Homework

### 2016-07-02 Macro Impacts.tex
Stuff

\end{document}

>>>>

\pagebreak
\section{Comparison to ``Passage of Small BH...''}
Their considerations in the acoustic limit account for a body force generated by the gravitational pull of the miniature black hole. They discover that only supersonic blackholes would generate this type of radiation. Our calculations, on the other hand, seem independent of these considerations. In our case, the gravitational pull of something as dense as a Macro is not negligible, but should not generate as significant an effect this way. The principal mechanism for energy deposition is the scattering of matter off the macro. However, their methods do bring into question whether the free wave equation is appropriate. They also consider the transfer of energy due to pressure from the black hole to matter along its path. This is a different calculation from ours since black hole radiation is very weak, as opposed to collisions between baryonic matter.
\\\\
However, one key point is that they do neglect shear by using a scalar displacement potential $\psi$ below their equation (3). Moreover, they neglect the subtlety of the behavior of the collision near the boundary of the Earth.

\pagebreak
\section{Our Argument}
As a Macro passes through the earth, there are several phases to its journey. The first is its passage through the atmosphere. The second is its crossing the boundary from air to earth, which we suspect will be relatively uneventful, since the air is 1000$\times$ lower density than earth, and thus would displace relatively little of it. The third is the transit of the macro through the earth. The shockwave it produces should be generated primarily by elastic and inelastic scattering of baryonic matter off the Macro. If we estimate that the macro produces an initial overpressure in a tube of its own radius, we can calculate the initial overpressure from the total energy deposition and its cross section. Given that the macro is dense enough, its loss of momentum will be approximately linear, and we can approximate its energy loss as being approximately constant. Estimates have already been made of the stopping power, so the total energy deposition will just be the
\begin{align}
\abs{\td{E}{x}{}}h=E_{\te{total}}=\f{\lambda+2\mu}{K^2}4\pi^2p_0^2\sigma_Xh
\end{align}
whence the initial overpressure is
\begin{align}
p_0=\f{K}{2\pi}\sqrt{\abs{\td{E}{x}{}}\f{1}{\sigma_X(\lambda+2\mu)}}
\end{align}
It is not appropriate to use the linear regime until the overpressure is close to 0 compared to some pressure, which we suspect may be $p_{\te{non-linear}}\approx60\te{GPa}$. It is reasonable to assume that the elastic limit holds when the pressures are an order of magnitude smaller than $p_{\te{non-linear}}$, denoted $p_{\te{linear}}\approx6\te{GPa}$. (This stuff needs to be checked). Note that energy losses due to heating, i.e. anelastic frequency attenuation, will dilute the energy density of the shock. However, for a conservative  estimate, we only consider the geometric attenuation, which will dilute the energy density as $r^{-1}$, where $r$ is the radial distance from the Macro's trajectory to the shock front. The shape of the shockwave will rapidly achieve a right-triangular profile. Geometric considerations show that the overpressure will go as $r^{-1}$. Thus, suppose that the average pressure in the shock is $\bar p$. Then the average pressure at radius $r$ is given
\begin{align}
\bar p(r)=p_0\f{r_0+l}{r}\,.
\end{align}
The overpressure is then given by
\begin{align}
p=\bar p_{\te{linear}}\f{r-r_0}{\ell}\ps{\theta(r_0+\ell-r)-\theta(r+\ell)}\ps{\theta(z+h/2)-\theta(z-h/2)}
\end{align}
where $\ell$ is the radial length of the shock and $r_0$ is its base. We now calculate the total energy contained in this shock. Fourier transforming reveals
\begin{align}
\notag P&=\f{\bar p_{\te{linear}}}{k_r^2k_z\ell}\pi\sin\p{\f{h}{2}k_z}\ps{(\ell+r_0)(2\sqrt{2} k_r\ell-\pi H_0(\sqrt{2} k_r(\ell+r_0))J_1(\sqrt{2}k_r(\ell+r_0))\right.\\&\left.+\pi(\ell+r_0)H_1(\sqrt{2}k_r(\ell+r_0))J_0(\sqrt{2}k_r(\ell+r_0))+\pi r_0 H_0(\sqrt{2}k_r r_0)J_1(\sqrt{2}k_r r_0)-\pi r_0 H_1(\sqrt{2} k_r r_0)J_0(\sqrt{2}k_r r_0)}
\end{align}
This reduces to, for the limit that $r_0\ll\lambda_{\te{attenuation}}$ 
\pagebreak
\section{What we still need to do}
What we've calculated is the the pressure from the total energy deposition. We need to figure out the total energy, pressure, and shape of the shock after it becomes sufficiently acoustic. It would also be good to know the velocity of the shock. From this, we can calculate the energy deposited in the measurable range.
\\\\
It appears as though *nobody* considers the shear waves... Should we?
\\\\
The gravitational effects can be taken into account as in the Black Hole paper.
\end{document}
